# Token allocation summary

**Earliest plausible date:** `r ifelse(TS<=0, paste(abs(TS-1), " BCE"), paste(TS," CE"))`  
**Latest plausible date:** `r ifelse(TE<=0, paste(abs(TE-1), " BCE"), paste(TE," CE"))`  
  
**Number of time intervals**: `r length(chips)`  
**Total number of tokens**: `r sum(chips)`  
**Approximate probability mass per token**:  `r paste0(round(1/sum(chips),2)*100, "%")`


```{r}
# Initialize an empty vector to store the formatted intervals
bins <- vector("character", length = length(bin.left))

# Loop over each pair of bin.left and bin.right
for (i in 1:length(bin.left)) {
  
  # Subtract 1 from negative or zero values
  left_val <- ifelse(bin.left[i] <= 0, bin.left[i] - 1, bin.left[i])
  right_val <- ifelse(bin.right[i] <= 0, bin.right[i] - 1, bin.right[i])
  
  # Determine the suffix based on the sign of left_val and right_val
  if (left_val < 0 && right_val < 0) {
     bins[i] <- paste0(abs(left_val), " - ", abs(right_val), " BCE")
  } else if (left_val > 0 && right_val > 0) {
    bins[i] <- paste0(abs(left_val), " - ", abs(right_val), " BCE")
  } else {
    # Mixed case: one negative, one positive
    bins[i] <- paste0(abs(left_val), " BCE"," - ", abs(right_val), " CE")
  }
}

# Combine the bins with the tokens (chips) into a data frame
sdf <- data.frame(Intervals = bins, Tokens = chips)
colnames(sdf) <- c( "Time intervals", "Allocated tokens")

# Display the result using knitr::kable
knitr::kable(sdf)
```


```{r, echo=FALSE}
# Define your condition here
if(length(fit)>1){show_distribution <- TRUE}else{show_distribution<-FALSE}
```

```{r,eval=show_distribution}
if(fit$limits[1, 1] == 0){
  x <- paste0("x")
  lower <- "`"}else{
    lower <- paste0("`", fit$limits[1, 1], " + ")}

if(fit$limits[1, 1] > 0){
  x <- paste0("(x-", fit$limits[1, 1],")")}
if(fit$limits[1, 1] < 0){
  x <- paste0("(x+", abs(fit$limits[1, 1]),")")}

xMirror <- paste0("(", fit$limits[1, 2],"-x)")
upper <- paste0("`", fit$limits[1, 2], " - ")

if(selected_distribution=="best"){
  selected_distribution<-unlist(fit$best.fitting)
}
```

```{asis, echo=show_distribution}
# Elicited cumulative probabilities

Implied cumulative probabilities used for distribution fitting are as follows:
```

```{r, eval=show_distribution}
expert <- 1
sf <- 3
mydf <- data.frame( fit$vals[expert, ], fit$probs[expert, ])

colnames(mydf) <- c( "$x$", "$P(X\\le x)$")
mydf[,1] <- to.BCECE(mydf[,1],toText=TRUE) 
mydf[,2] <- round(mydf[,2],2) 
knitr::kable(mydf)
```

```{asis, echo=show_distribution}
# Selected Fit
```

`r if(length(fit)==1){"Distribution not fitted. Insufficient number of bins contain tokens or too few tokens."}`

```{r, echo = FALSE,eval=show_distribution}

### Normal

if(selected_distribution=="normal"){
  mu <- signif(fit$Normal[1, 1],6)
  sig <- signif(fit$Normal[1, 2],6)
  
  equation <- paste0("$f_X(x)=\\frac{1}{\\sqrt{2\\pi\\sigma^2}} 
\\exp\\left(-\\frac{1}{2 \\sigma^2}(x - \\mu)^2\\right),\\quad -\\infty<x<\\infty,$")
  parameters<-paste0("$\\mu = ", mu,",$ $\\sigma = ", sig, "$")
  label = "Normal"

### Student-T

}else if(selected_distribution=="t"){

   m <- signif(fit$Student.t[1, 1],6)
   s <- signif(fit$Student.t[1, 2],6)
   tdf <- fit$Student.t[1, 3]

    equation <- paste0("$$
f_X(x) = \\frac{\\Gamma((\\nu + 1)/2)}{\\Gamma(\\nu/2)\\sigma\\sqrt{\\nu \\pi}} \\left(1 + \\frac{1}{\\nu}\\left(\\frac{x - \\mu}{\\sigma}\\right)^2\\right)^{-(\\nu + 1)/2},\\quad -\\infty<x<\\infty,
$$") 
    parameters <- paste0("$\\nu = ", tdf,",$ $\\mu = ", m,",$ $\\sigma  = ", s, "$")
    label="Student-t"
}else if(selected_distribution=="skewnormal"){

    xi <- signif(fit$Skewnormal[1, 1], 6)
    omega <- signif(fit$Skewnormal[1, 2], 6)
    alpha <- signif(fit$Skewnormal[1, 3], 6)   
    equation <- paste0("$f_X(x)=\\frac{2}{\\omega}\\phi\\left(\\frac{x-\\xi}{\\omega}\\right)\\Phi\\left(\\alpha\\left(\\frac{x-\\xi}{\\omega}\\right)\\right),\\quad -\\infty<x<\\infty,$   \n
where $\\phi(.)$ and $\\Phi(.)$ are the probability density function and cumulative distribution function respectively of the standard normal distribution")
    parameters=paste0("$\\xi = ", xi,",$ $\\omega  = ", omega, "$, $\\alpha  = ", alpha, "$")
    label="Skew Normal"

### Log Normal:
}else if(selected_distribution=="lognormal"){

  mu <- signif(fit$Log.normal[1, 1], 6)
  sigsq <- signif(fit$Log.normal[1, 2]^2, 6)  
  
  equation <- paste0("$$f_X(x) = \\frac{1}{", x, "} \\times \\frac{1}{\\sqrt{2\\pi\\sigma^2}} 
\\exp\\left(-\\frac{1}{2\\sigma^2}(\\ln ", x,"  - \\mu)^2\\right), \\quad x >", fit$limits[1, 1],"$$\n $f_X(x)=0$ otherwise.\n  ")
  
  if(fit$limits[1, 1] != 0){
    shiftLognormal <- paste0("Log normal distribution shifted to have support over the interval $(",
                               fit$limits[1, 1],
                               ",\\, \\infty )$.")
  }else{
    shiftLognormal <- NULL
  }
  equation = paste(equation, shiftLognormal)
  parameters=paste0("$\\mu = ", mu,"$ $\\sigma^2  = ", sigsq, "$")
  label="Log Normal"
}else if(selected_distribution=="gamma"){
  
  shape <- signif(fit$Gamma[1, 1], 6)
  rate <- signif(fit$Gamma[1, 2], 6)  
  
  equation <- paste0("$$f_X(x) =\\frac{\\beta ^ {\\alpha}}{\\Gamma(\\alpha)}",  x,
"^{\\alpha - 1} \\exp\\left(- \\beta ", x,"\\right), \\quad x >", fit$limits[1, 1],"$$ and $f_X(x)=0$ otherwise")
  
 
  
  samplingGamma <- paste0(lower, " rgamma(n = 1000, shape = ", shape,", rate = ",
rate,")`" )
  
  samplingGammaText <- "Sample `n = 1000` random values with the command"
  
   if(fit$limits[1, 1] != 0){
    shiftGamma <- paste0("Gamma distribution shifted to have support over the interval $(",
                               fit$limits[1, 1],
                               ",\\, \\infty )$.")
  }else{
    shiftGamma <- NULL
  }
  
  equation <- paste0("$$f_X(x) = \\frac{1}{", x, "} \\times \\frac{1}{\\sqrt{2\\pi\\sigma^2}} 
\\exp\\left(-\\frac{1}{2\\sigma^2}(\\ln ", x,"  - \\mu)^2\\right), \\quad x >", fit$limits[1, 1],"$$\n $f_X(x)=0$ otherwise.\n  ")
  
 
  equation = paste(equation, shiftGamma)
  parameters=paste0("$\\alpha = ", shape,"$ $\\beta  = ", rate, "$")
  label="Gamma"
}else if(selected_distribution=="logt"){
  m <- signif(fit$Log.Student.t[1, 1], 6)
  s <- signif(fit$Log.Student.t[1, 2], 6)
  tdf <- fit$Log.Student.t[1, 3]
  
  equation<- paste0("$$f_X(x) =\\frac{1}{", x, "} \\times \\frac{\\Gamma((\\nu + 1)/2)}{\\Gamma(\\nu/2)\\times\\sigma\\times \\sqrt{\\nu \\pi}} \\left(1 + \\frac{1}{\\nu}\\left(\\frac{\\ln ", x, " - \\mu}{\\sigma}\\right)^2\\right)^{-(\\nu + 1)/2}, \\quad x >", fit$limits[1, 1],"$$ and $f_X(x)=0$ otherwise.\n")
  
 
  
  samplingLogStudentT <- paste0(lower, " exp(", m, " + ", s, " * rt(n = 1000, df = ", tdf,"))`" )
  
  samplingLogStudentTText <- "Sample `n = 1000` random values with the command"
  
  if(fit$limits[1, 1] != 0){
    shiftLogStudentT <- paste0("Log Student-$t$ distribution shifted to have support over the interval $(",
                               fit$limits[1, 1],
                               ",\\, \\infty )$.")
  }else{
    shiftLogStudentT <- NULL
  }
  equation = paste(equation, shiftLogStudentT)
  parameters=paste0("$\\nu = ", tdf,"$ $\\mu  = ", m, "$ $\\sigma = ", s , ".$")
  label="Log Studnet-t"
}else if (selected_distribution=="beta"){
  if(fit$limits[1, 1] == 0)
  x <- paste0("x")
if(fit$limits[1, 1] > 0)
  x <- paste0("x-", fit$limits[1, 1])
if(fit$limits[1, 1] < 0)
  x <- paste0("x+", abs(fit$limits[1, 1]))
if(fit$limits[1, 2] < Inf & fit$limits[1, 1] > -Inf){
  r <- fit$limits[1, 2] - fit$limits[1, 1]
  if(r !=1){
  mult = paste0(r, " *")}else{
    mult = ""
  }
}


shape1 <- signif(fit$Beta[1, 1], 6)
shape2 <- signif(fit$Beta[1, 2], 6)

if(r == 1 & fit$limits[1, 1] == 0){
  equationBeta <- paste0("$$f_X(x) = \\frac{\\Gamma(\\alpha + \\beta)}{\\Gamma(\\alpha)\\Gamma(\\beta)}x ^{\\alpha - 1} \\left(1 - x\\right)^{\\beta - 1}, \\quad  0 < x < 1, $$ and $f_X(x) = 0$ otherwise.")
  scalingBeta <- NULL
  }
  if(r == 1 & fit$limits[expert, 1] != 0){
    equationBeta <- paste0("$$f_X(x) = \\frac{\\Gamma(\\alpha + \\beta)}{\\Gamma(\\alpha)\\Gamma(\\beta)} \\left(", x,"\\right) ^{\\alpha - 1} \\left(1 - \\left(", x,"\\right)\\right)^{\\beta - 1}, \\quad  ", fit$limits[1, 1]," < x <", fit$limits[1, 2],",$$ and $f_X(x) = 0$ otherwise.")
    scalingBeta <- paste0("Fitted beta distribution is scaled to the interval [",
                          fit$limits[1, 1],
                          ", ",
                          fit$limits[1, 2],
                          "].")
  }
  
  
  if(r !=1){
    equationBeta <- paste0("$$f_X(x) = \\frac{1}{", r, "}\\times\\frac{\\Gamma(\\alpha + \\beta)}{\\Gamma(\\alpha)\\Gamma(\\beta)} \\left(\\frac{", x,"}{", r,"}\\right) ^{\\alpha - 1} \\left(1 - \\left(\\frac{", x,"}{", r,"}\\right)\\right)^{\\beta - 1}, \\quad  ", fit$limits[1, 1]," < x <", fit$limits[1, 2],",$$ and $f_X(x) = 0$ otherwise.")
    scalingBeta <- paste0("Fitted beta distribution is scaled to the interval [",
                          fit$limits[1, 1],
                          ", ",
                          fit$limits[1, 2],
                          "].")
  equation<-paste(equationBeta,scalingBeta)
  #parameters<-paste0("$\\alpha = ", shape1, ",$ $ \\beta = ", shape2, "$")
  parameters=paste0("$\\alpha = ", shape1,"$ $\\beta  = ", shape2, "$")
  #parameters=""
  label="Beta"
  }
}else if(selected_distribution=="mirrorgamma"){
  shape <- signif(fit$mirrorgamma[1, 1], 6)
  rate <- signif(fit$mirrorgamma[1, 2], 6)  
  
  equation <- paste0("$$f_X(x) =\\frac{\\beta ^ {\\alpha}}{\\Gamma(\\alpha)}",  xMirror,
"^{\\alpha - 1} \\exp\\left(- \\beta ", xMirror,"\\right), \\quad x <", fit$limits[1, 2],"$$ and $f_X(x)=0$ otherwise.\n  ")
  
 
  
  samplingMirrorGamma <- paste0(upper, " rgamma(n = 1000, shape = ", shape,", rate = ",
rate,")`" )
  
  samplingMirrorGammaText <- "Sample `n = 1000` random values with the command"
  

    shiftMirrorGamma <- paste0("Gamma distribution fitted to ", fit$limits[1, 2]," - $X$.")
    
  equation<- paste0(equation, shiftMirrorGamma )
  #parameters=paste0("$\\alpha = ", shape1,"$ $\\beta  = ", shape2, "$")
  parameters=paste0("$\\alpha = ", shape,"$ $\\beta  = ", rate, "$")
  label="Mirror Gamma"
}else if(selected_distribution=="mirrorlognormal"){
  mu <- signif(fit$mirrorlognormal[1, 1], 6)
  sigsq <- signif(fit$mirrorlognormal[1, 2]^2, 6)  
  
  equationMirrorLogNormal <- paste0("$$f_X(x) = \\frac{1}{", xMirror, "} \\times \\frac{1}{\\sqrt{2\\pi\\sigma^2}} 
\\exp\\left(-\\frac{1}{2\\sigma^2}(\\ln ", xMirror,"  - \\mu)^2\\right), \\quad x <", fit$limits[1, 2],"$$ and $f_X(x)=0$ otherwise.\n  ")
  
 
  
  samplingMirrorLogNormal <- paste0(upper, " rlnorm(n = 1000, meanlog = ", mu,", sdlog = sqrt(",
sigsq,"))`" )
  
  samplingMirrorLogNormalText <- "Sample `n = 1000` random values with the command"
  
   shiftMirrorLognormal <- paste0("Normal distribution fitted to $\\log$ (  ", fit$limits[1, 2]," - $X$).")
   equation<-paste0(equationMirrorLogNormal,shiftMirrorLognormal)
   parameters <-paste0("$\\mu = ", mu,"$ $\\sigma^2  = ", sigsq, "$")
   label="Mirror Log Normal"
}else if(selected_distribution=="mirrorlogt"){
  
  m <- signif(fit$mirrorlogt[1, 1], 6)
  s <- signif(fit$mirrorlogt[1, 2], 6)
  tdf <- fit$mirrorlogt[1, 3]
  
  equationMirrorLogStudentT <- paste0("$$f_X(x) =\\frac{1}{", xMirror, "} \\times \\frac{\\Gamma((\\nu + 1)/2)}{\\Gamma(\\nu/2)\\times\\sigma\\times \\sqrt{\\nu \\pi}} \\left(1 + \\frac{1}{\\nu}\\left(\\frac{\\ln ", xMirror, " - \\mu}{\\sigma}\\right)^2\\right)^{-(\\nu + 1)/2}, \\quad x <", fit$limits[1, 2],"$$ and $f_X(x)=0$ otherwise.\n  ")
  
 
  
  samplingMirrorLogStudentT <- paste0(upper, " exp(", m, " + ", s, " * rt(n = 1000, df = ", tdf,"))`" )
  
  samplingMirrorLogStudentTText <- "Sample `n = 1000` random values with the command"

   shiftMirrorLogStudentT <- paste0("Student-$t$ distribution fitted to $\\log$ (  ", fit$limits[1, 2]," - $X$).")
   
   equation<-paste0(equationMirrorLogStudentT,shiftMirrorLogStudentT)
   parameters <- paste0("$\\nu = ", tdf,"$ $\\mu  = ", m, "$ $\\sigma = ", s , "$")
   label <- "Mirror Log Student-t"
}else if(selected_distribution=="hist"){
  equation=""
  parameters=""
  label<-"histogram"
}

```


```{r, echo=FALSE, results='asis'}

if (show_distribution) {
  if(grepl("NA", parameters)==TRUE){
     cat(knitr::knit_child(text = "**Distribution:** `r label`  
                        Distribution not fitted - insufficient number of tokens or bins with tokens provided." , quiet = TRUE))
  show_distribution <- FALSE
  }else{
  
  # Create the template string
  # Note: The \n is used for line breaks since we are inside a string
  content <- "
**Distribution:** `r label`  
**Parameters:** `r parameters`  
  
**Equation**: `r equation`
"
  
  # Knit the string so the `r ` expressions are evaluated
  cat(knitr::knit_child(text = content, quiet = TRUE))
  }
}
```

```{r fig.width=6.5, fig.height=4,eval=show_distribution}

# lpw = 1,
#                    fs = 12,
#                    lwd = 1,



plotfit(fit, d = selected_distribution,
        ql=ql,qu=qu,
        xl=xl, xu=xu, 
        fs=11,
        xlab=xlab,
        startDate=startDate,
        endDate=endDate,
        nBins=nBins,
        ybreaks=ybreaks,
        chips=chips,
        lwd=0.1)


```

```{asis, echo=show_distribution}

All parameter values reported to 6 significant figures. Where relevant, negative parameter values in the equations map onto the BCE/CE scale, with a negative year -x = |(-x-1)| BCE.  


# Feedback for the fit
```

```{r results='asis',eval=show_distribution}


fqc<-c(0.1,0.9,0.5)  
bin.left<-bin.left[min(which(chips!=0))]
bin.right<-bin.right[max(which(chips!=0))]
fpc<-c(bin.left,bin.right)

fbs<-generateFeedbackSummary(fit,dist=selected_distribution,fqc=fqc,fpc=fpc)
feedbackText(fbs)
```

```{r echo=FALSE}

if(nchar(user_notes)>0){notes=TRUE}else{notes=FALSE}

```
```{asis, echo=notes}

# Post-elicitation notes
```

```{r echo=FALSE, results='asis'}

cat(user_notes)

```

```{asis, echo=show_distribution}

# Customised feedback
```

```{r results='asis',eval=show_distribution}

fbs<-generateFeedbackSummary(fit,dist=selected_distribution,fqc=fq,fpc=fp)

cat("**Additional feedback for selected quantiles**\n\n")
fbs$values[,2]<-round(fbs$values[,2],1)
fbs$values[,1]<-to.BCECE(fbs$values[,1],toText=TRUE) 
knitr::kable(fbs$values)
cat("**Additional feedback for selected probabilities**\n\n")
fbs$probs[,1]<-round(fbs$probs[,1],2)
fbs$probs[,2]<-to.BCECE(fbs$probs[,2],toText=TRUE) 
knitr::kable(fbs$probs)

```

```{asis, echo=show_distribution}

Probabilities given either to 2 decimal places or as percentage.  
```



