### Portfolio of Evidence:

`r PoE`


### Plausible Date Range  

##### **Earliest plausible date:** `r ifelse(TS<=0, paste(abs(TS-1), " BCE"), paste(TS," CE"))` 
##### **Latest plausible date:** `r ifelse(TE<=0, paste(abs(TE-1), " BCE"), paste(TE," CE"))`

### Token allocation summary

##### **Total number of tokens**: `r sum(chips)`
##### **Probability per token**:  `r 1/sum(chips)`

```{r}
if(roulette == TRUE){

# Initialize an empty vector to store the formatted intervals
bins <- vector("character", length = length(bin.left))

# Loop over each pair of bin.left and bin.right
for (i in 1:length(bin.left)) {
  
  # Subtract 1 from negative or zero values
  left_val <- ifelse(bin.left[i] <= 0, bin.left[i] - 1, bin.left[i])
  right_val <- ifelse(bin.right[i] <= 0, bin.right[i] - 1, bin.right[i])
  
  # Determine the suffix based on the sign of left_val and right_val
  if (left_val < 0 && right_val < 0) {
     bins[i] <- paste0(abs(left_val), " - ", abs(right_val), " BCE")
  } else if (left_val > 0 && right_val > 0) {
    bins[i] <- paste0(abs(left_val), " - ", abs(right_val), " BCE")
  } else {
    # Mixed case: one negative, one positive
    bins[i] <- paste0(abs(left_val), " BCE"," - ", abs(right_val), " CE")
  }
}

# Combine the bins with the tokens (chips) into a data frame
sdf <- data.frame(Intervals = bins, Tokens = chips)
colnames(sdf) <- c( "Time intervals", "Allocated tokens")

# Display the result using knitr::kable
knitr::kable(sdf)
}
```

```{r}
source("extra_functions/checkJudgementsValid.r")
source("extra_functions/feedback.r")
source("extra_functions/feedbacksingle.r")
source("extra_functions/qhist.r")
source("extra_functions/phist.r")
source("extra_functions/fitdist2.r")
source("extra_functions/normal.error.r")
source("extra_functions/logt.error.r")
source("extra_functions/gamma.error.r")
source("extra_functions/tError.R")
source("extra_functions/exponential.error.R")
source("extra_functions/lognormal.error.R")
source("extra_functions/plotfit.R")
source("extra_functions/makeSingleExpertPlot.R")
source("extra_functions/dhist.R")
source("extra_functions/fitBspline.r")
source("extra_functions/makeCDFPlot.R")
source("extra_functions/cdfHelperfunctions.R")
source("extra_functions/generateFeedbackSummary.R")
source("extra_functions/feedbackText.R")

```

### Elicited cumulative probabilities

```{asis, echo = roulette}
Implied cumulative probabilities used for distribution fitting are as follows
```

```{r}
expert <- 1
sf <- 3
mydf <- data.frame( fit$vals[expert, ], fit$probs[expert, ])

colnames(mydf) <- c( "$x$", "$P(X\\le x)$")
knitr::kable(mydf)
```

```{r}
if(fit$limits[expert, 1] == 0){
  x <- paste0("x")
  lower <- "`"}else{
    lower <- paste0("`", fit$limits[expert, 1], " + ")}

if(fit$limits[expert, 1] > 0){
  x <- paste0("(x-", fit$limits[expert, 1],")")}
if(fit$limits[expert, 1] < 0){
  x <- paste0("(x+", abs(fit$limits[expert, 1]),")")}

xMirror <- paste0("(", fit$limits[expert, 2],"-x)")
upper <- paste0("`", fit$limits[expert, 2], " - ")
```

```{r}
lx <- min(fit$vals[expert, ])
ux <- max(fit$vals[expert, ])
```

```{r}
judgementsDF <- data.frame(judgement = c("lower limit",
                                         "upper limit",
                                         "smallest elicited probability",
                                         "largest elicited probability"
                                         )
                           ,
                           value = c(fit$limits[expert, "lower"],
                                         fit$limits[expert, "upper"],
                                         min(fit$probs[expert, ]),
                                          max(fit$probs[expert, ])
                                         )
                           )
                                         
                                             
                                         
                                        
```

```{r, eval = any(is.na(fit$ssq[expert, ]))}
knitr::kable(judgementsDF)
```

All parameter values reported to 3 significant figures.

### Selected Fit


```{r}
#fit$ssq[expert, selected_distribution]
#if(!is.na(fit$ssq[expert, "normal"])){
plotfit(fit, d = selected_distribution,
        ql=ql,qu=qu,
        xl=xl, xu=xu, 
        fs=fs,
        xlab=xlab,
        startDate=startDate,
        endDate=endDate,
        nBins=nBins,
        ybreaks=ybreaks,
        chips=chips)
#plotfit(fit, d = "normal")
#}
```

### Feedback for the fit
```{r}
fqc<-c(0.1,0.9,0.5)  
bin.left<-bin.left[min(which(chips!=0))]
bin.right<-bin.right[max(which(chips!=0))]
fpc<-c(bin.left,bin.right)

fbs<-generateFeedbackSummary(fit,dist=selected_distribution,fqc=fqc,fpc=fpc)
feedbackText(fbs)
```

### Additional feedback

```{r}

fbs<-generateFeedbackSummary(fit,dist=selected_distribution,fqc=fq,fpc=fp)

knitr::kable(fbs$values)
knitr::kable(fbs$probs)


```

