# Token allocation summary

**Earliest plausible date:** `r ifelse(TS<=0, paste(abs(TS-1), " BCE"), paste(TS," CE"))`  
**Latest plausible date:** `r ifelse(TE<=0, paste(abs(TE-1), " BCE"), paste(TE," CE"))`  
  
**Number of time intervals**: `r length(chips)`  
**Total number of tokens**: `r sum(chips)`  
**Approximate probability mass per token**:  `r paste(round(1/sum(chips),2)*100, "%")`

```{r}
# Initialize an empty vector to store the formatted intervals
bins <- vector("character", length = length(bin.left))

# Loop over each pair of bin.left and bin.right
for (i in 1:length(bin.left)) {
  
  # Subtract 1 from negative or zero values
  left_val <- ifelse(bin.left[i] <= 0, bin.left[i] - 1, bin.left[i])
  right_val <- ifelse(bin.right[i] <= 0, bin.right[i] - 1, bin.right[i])
  
  # Determine the suffix based on the sign of left_val and right_val
  if (left_val < 0 && right_val < 0) {
     bins[i] <- paste0(abs(left_val), " - ", abs(right_val), " BCE")
  } else if (left_val > 0 && right_val > 0) {
    bins[i] <- paste0(abs(left_val), " - ", abs(right_val), " BCE")
  } else {
    # Mixed case: one negative, one positive
    bins[i] <- paste0(abs(left_val), " BCE"," - ", abs(right_val), " CE")
  }
}

# Combine the bins with the tokens (chips) into a data frame
sdf <- data.frame(Intervals = bins, Tokens = chips)
colnames(sdf) <- c( "Time intervals", "Allocated tokens")

# Display the result using knitr::kable
knitr::kable(sdf)
```






# Selected Fit: 

```{r, echo = FALSE}

### Normal

if(selected_distribution=="normal"){
  mu <- signif(fit$Normal[1, 1],5)
  sig <- signif(fit$Normal[1, 2],5)
  
  equation <- paste0("$f_X(x)=\\frac{1}{\\sqrt{2\\pi\\sigma^2}} 
\\exp\\left(-\\frac{1}{2 \\sigma^2}(x - \\mu)^2\\right),\\quad -\\infty<x<\\infty,$")
  parameters<-paste0("$\\mu = ", mu,",$ $\\sigma = ", sig, "$")
  label = "Normal"

### Student-T

}else if(selected_distribution=="t"){

   m <- signif(fit$Student.t[1, 1],5)
   s <- signif(fit$Student.t[1, 2],5)
   tdf <- fit$Student.t[1, 3]

    equation <- paste0("$$
f_X(x) = \\frac{\\Gamma((\\nu + 1)/2)}{\\Gamma(\\nu/2)\\sigma\\sqrt{\\nu \\pi}} \\left(1 + \\frac{1}{\\nu}\\left(\\frac{x - \\mu}{\\sigma}\\right)^2\\right)^{-(\\nu + 1)/2},\\quad -\\infty<x<\\infty,
$$") 
    parameters <- paste0("$\\nu = ", tdf,",$ $\\mu = ", m,",$ $\\sigma  = ", s, "$")
    label="Student-t"
}else if(selected_distribution=="skewnormal"){

    xi <- signif(fit$Skewnormal[1, 1], 5)
    omega <- signif(fit$Skewnormal[1, 2], 5)
    alpha <- signif(fit$Skewnormal[1, 3], 5)   
    equation <- paste0("$f_X(x)=\\frac{2}{\\omega}\\phi\\left(\\frac{x-\\xi}{\\omega}\\right)\\Phi\\left(\\alpha\\left(\\frac{x-\\xi}{\\omega}\\right)\\right),\\quad -\\infty<x<\\infty,$   \n
where $\\phi(.)$ and $\\Phi(.)$ are the probability density function and cumulative distribution function respectively of the standard normal distribution")
    parameters=paste0("$\\xi = ", xi,",$ $\\omega  = ", omega, "$, $\\alpha  = ", alpha, "$")
    label="Skew Normal"

### Log Normal:
}else if(selected_distribution=="lognormal"){

  mu <- signif(fit$Log.normal[1, 1], 5)
  sigsq <- signif(fit$Log.normal[1, 2]^2, 5)  
  
  equation <- paste0("$$f_X(x) = \\frac{1}{", x, "} \\times \\frac{1}{\\sqrt{2\\pi\\sigma^2}} 
\\exp\\left(-\\frac{1}{2\\sigma^2}(\\ln ", x,"  - \\mu)^2\\right), \\quad x >", fit$limits[1, 1],"$$ and $f_X(x)=0$ otherwise, 
with $$\\mu = ", mu,"$$ $$\\sigma^2  = ", sigsq, "$$")
  
  if(fit$limits[1, 1] != 0){
    shiftLognormal <- paste0("Log normal distribution shifted to have support over the interval $(",
                               fit$limits[1, 1],
                               ",\\, \\infty )$.")
  }else{
    shiftLognormal <- NULL
  }
  equation = paste(equation, shiftLognormal)
  parameters=""
  label="Log Normal"
}

```
**Distribution:** `r paste(label)`  
**Parameters:** `r paste(parameters)`  
  
**Equation**: `r paste(equation)`

```{r fig.width=6.5, fig.height=4}

plotfit(fit, d = selected_distribution,
        ql=ql,qu=qu,
        xl=xl, xu=xu, 
        fs=fs,
        xlab=xlab,
        startDate=startDate,
        endDate=endDate,
        nBins=nBins,
        ybreaks=ybreaks,
        chips=chips)

```

# Feedback for the fit

```{r results='asis'}
fqc<-c(0.1,0.9,0.5)  
bin.left<-bin.left[min(which(chips!=0))]
bin.right<-bin.right[max(which(chips!=0))]
fpc<-c(bin.left,bin.right)

fbs<-generateFeedbackSummary(fit,dist=selected_distribution,fqc=fqc,fpc=fpc)
feedbackText(fbs)
```

# Post-elicitation notes

```{r echo=FALSE, results='asis'}

cat(user_notes)

```

# Additional Information

## Custom feedback

```{r results='asis'}

fbs<-generateFeedbackSummary(fit,dist=selected_distribution,fqc=fq,fpc=fp)

cat("**Additional feedback for selected quantiles**\n\n")
knitr::kable(round(fbs$values),2)
cat("**Additional feedback for selected probabilities**\n\n")
knitr::kable(round(fbs$probs,2))

```
## Elicited cumulative probabilities

```{asis, echo = roulette}
Implied cumulative probabilities used for distribution fitting are as follows:
```

```{r}
expert <- 1
sf <- 3
mydf <- data.frame( fit$vals[expert, ], fit$probs[expert, ])

colnames(mydf) <- c( "$x$", "$P(X\\le x)$")
knitr::kable(round(mydf,2))
```

  

All parameter values reported to 3 significant figures.   

Probabiliites provided either to 2 decimal places or as percentage.  




